%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.21in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}

%\documentclass{article}
\usepackage{booktabs}% http://ctan.org/pkg/booktabs


\newcommand{\tabitem}{~~\llap{\textbullet}~~}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins

% title on top of the document
\maintitle{Parth Patel}{August 01, 1994}{Last update on \today }

\nobreakvspace{0.4em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:patelparth622.at.gmail.dot.com}{patelparth622\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}1 (626)493-3759\sbull
{\newnums \href{https://github.com/parthp2}{parthp2 (Github)}\sbull
{\newnums \href{http://www.patelparth.net/}{Portfolio}\sbull
{\mewmums \href{https://www.linkedin.com/in/parthpatelp2/}{www.linkedin.com/in/parthpatelp2}
\\
{Los Angeles\sbull
California\sbull
United States
}
\spacedhrule{0.0em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Experience}



\headedsection  % sets the header for the section and includes any subsections
  {\href{http://web.calstatela.edu/library/}{University Library, Cal State LA}}
  {\textsc{Los Angeles, United States}} {%
  \headedsubsection
    {Web Developer Assistant}
    {March \apo17 -- present}
    {\bodytext
    {
    \begin{itemize}
        \item Works with library web team on re-designing of  Library website and to add some additional features to the website. Responsible for developing front-end to create UI for web and mobile optimized formats.
        \item Created interactive floor maps using Javascript and relational database to give detailed information and to show available library resources on each floor.
        \item Manage back-end of website, construct online forms and conduct online assessments, analytics and surveys.Create visualization effects and animations of web components and develop images for web optimization formats.
        \item \textbf{\small{ PHP |HTML5 | CSS3 | AJAX | JQuery | Dropal | MySQL | RaphaelJS | Photoshop | MagnificPop  }}
    \end{itemize}}}
}

\headedsection  % sets the header for a subsection and contains usually body text
  {\href{https://www.linkedin.com/company/incisive-web-solution-pvt-ltd-/}{Incisive Web Solution Pvt. Ltd.}}
  {\textsc{Gujarat, India}} {%
  \headedsubsection
    {Jr. Software Developer}
    {June \apo15 -- May \apo16}
    {\bodytext{
    \begin{itemize}
        \item Involved with all phases of Software development from initial concepts, design, development, testing and deployment. 
        \item Participated in brainstorming and user feedback sessions to gather input to apply changes for prototype iterations. 
        \item Designed and developed SaaS based product as per client requirement.
        \item  Worked in a team to deliver End-to-End development of software solutions across multiple stages of Software Development Life.
        \item \textbf{\small{ Java | Hibernate | Spring MVC | MySQL | Javascript | REST API | Junit | TestNG | NodeJS | GIT  }}
    \end{itemize}}}
}

\headedsection  % sets the header for a subsection and contains usually body text
  {\href{https://www.linkedin.com/company/incisive-web-solution-pvt-ltd-/}{Incisive Web Solution Pvt. Ltd.}}
  {\textsc{Gujarat, India}} {%
  \headedsubsection
    {Java Developer Intern}
    {June \apo14 -- May \apo15}
    {\bodytext{
    \begin{itemize}
        \item Worked on different e-commerce web projects for local markets and Maintain and optimize current ongoing SAAS projects and perform time to time testing and updates.
        \item Worked with senior level developers to create projects from scratch, developing web design templets, database schema, DFD, ER diagrams.
        \item \textbf{\small{ PHP | CakePHP | Java | HTML5 | CSS3 | JSP | Javascript }}
    \end{itemize}}}
}

\spacedhrule{0.0em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{http://www.calstatela.edu/}{California State University,Los Angeles} }
  {\textsc{California, United States}} {%
  \headedsubsection
    {Master of Science in Computer Science}
    {Graduate - August \apo18}
    {}
}


\headedsection
  {\href{https://www.gtu.ac.in/}{Gujarat Technological University } }
  {\textsc{Gujarat, India}} {%
  \headedsubsection
    {Bachelor of Engineering in Computer Engineering}
    {Graduated - May \apo15}
    {}
}

\spacedhrule{0.0em}{-0.4em}

\roottitle{Skills}
{\bodytext{
  \begin{tabular}{ll}
    %\midrule
    \tabitem \textbf{Programming Languages} & Java, C++, Android, Python, Haskell \\[.1\normalbaselineskip]
    \tabitem \textbf{Web Technologies} & Javascript, NodeJS-Express, JAX-WS, AJAX, Spring, Rest Web-Services \\[.1\normalbaselineskip]
    \tabitem \textbf{Front-end Technologies} & Html 5, CSS, AngularJs, VueJS, Bootstrap, React, Redux, JSP, XML \\[.1\normalbaselineskip]
    \tabitem \textbf{Databases/Middleware} & MySQL, MongoDB, Postgre SQL, AWS RDS, Oracle, RabbitMQ, Redis \\[.1\normalbaselineskip]
    \tabitem \textbf{Testing Tools and Frameworks} \hspace{.3cm}  &  JMeter, JUnit, TestNG, MockTest, Jasmine, Mocha, Selenium \\[.1\normalbaselineskip]
    \tabitem \textbf{Cloud Technologies} &  AWS, Heroku, Google App Engine, Google Compute Engine, IBM Bluemix \\[.1\normalbaselineskip]
    \tabitem \textbf{SCM and Versioning Tools} & Git, Gradle, Maven, Intellij, Eclipse , Android Studio, Jupyter Notebook \\[.1\normalbaselineskip]
    
  \end{tabular}
}}

\spacedhrule{0.0em}{-0.4em}

\roottitle{Academic Projects}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/parthp2/techit-server-java}{TechIt}
  \textbf{
  \small{(J2EE | Spring MVC | Hibernate | Maven | REST API's | MySQL | NodeJs | Angular | MongoDB)}}}
  {} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Designed and developed TechIt using 3 tier architecture for ECST's TechOPs.
        \item Create order and assignment to designated team, prioritize and update status of order. Multiple administrative access to manage system.
    \end{itemize}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/parthp2/Mars-Rover-Simulation}{Mars Rover Simulation}
  \textbf{
  \small{(NodeJS | ExpressJS | JSON | REST API | Java | J2EE)}}}
  {} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item J2EE-based project simulating Mars rovers on a planet surface, runs on a server built with Node and Express. Collaborated with three different teams to share coordinates of each rover via REST service. Uses live communication server to ensure accurate path finding.
        \item Build an AI for ROVER movement and science harnessing based on coordinates and data received from REST server.
    \end{itemize}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/parthp2/TodoApp}{Collaborative To-Do App}
  \textbf{
  \small{(NodeJs | VueJs | Bulma | Web Sockets | MongoDB | HTML | CSS)}}}
  {} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Collaborative web application that allow users to create projects and to-do's within projects.
        \item Using web sockets made real time web application to display, add, remove and to mark todo done and undone for all the projects and todos.
    \end{itemize}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/parthp2/ScoreTracker-CS5540}{ScoreTracker Android App}
  \textbf{
  \small{(Android Studio | Google Firebase | Java | REST API | JSP | Thread | Gradle | XML)}}}
  {} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Android application that provides real-time score for MLB, NBA using Firebase Job Dispatcher, Job Scheduler and live score usingREST API calls to a live server.
        \item Embedded map with Google Maps Directions API showing direction from current location to match venue.
    \end{itemize}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/parthp2/House-Sales-Prediction}{House Sales Prediction}
  \textbf{
  \small{(Python | Pandas | NumPy | Scikit-learn | Linear Regression | KNN | Random forest | PCA)}}}
  {} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Using various machine learning algorithms such as Linear Regression, Random Forest and Polynomial Regression and techniques such as PCA, Data normalization, Data Scaling designed a prediction model to predict sale price of a house in king county based on various features.
        \item Provides a comprehensive insight into the data and feature correlation using Mat plotlib, Heatmap and Scatter plot.
    \end{itemize}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/parthp2/CS3220_Spring_2017/tree/CS3220/HW7}{File Management System}
  \textbf{
  \small{(JSP | Hibernate | Ajax | MySQL | HTML | CSS | Javascript)}}}
  {} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Developed a web application using hibernate framework and mysql database to maintain files.
        \item Application let users search for new files, upload new files, share and download files, create folders, login and logout.
    \end{itemize}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/parthp2/Bull-and-Fool}{Bull and Fool}
  \textbf{
  \small{(Java | JavaFx | CSS )}}}
  {} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Developed desktop game bull and fool, bull try to catch fool in maze map and fool move by direction key of keyboard.
    \end{itemize}}}
}

\end{document}
\documentclass[oneside]{book}